---
title: "chicago_bicycle_company.Rmd"
author: "Vinay_kumar"
date: "2023-02-18"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

##Setting up my environment Notes : setting up my R environment by loading the 'tidyverse' ,'lubridate' and 'readr' packages

```{r loading packages}
library(tidyverse)
library(lubridate)
library(readr)

```

## Loading Data In R

```{r loading data, message=FALSE, warning=TRUE}
feb_2022 <- read_csv("Desktop/case study 1/202202.csv")
mar_2022 <- read_csv("Desktop/case study 1/202203.csv")
apr_2022 <- read_csv("Desktop/case study 1/202204.csv")
may_2022 <- read_csv("Desktop/case study 1/202205.csv")
jun_2022 <- read_csv("Desktop/case study 1/202206.csv")
jul_2022 <- read_csv("Desktop/case study 1/202207.csv")
aug_2022 <- read_csv("Desktop/case study 1/202208.csv")
sep_2022 <- read_csv("Desktop/case study 1/202209.csv")
oct_2022 <- read_csv("Desktop/case study 1/202210.csv")
nov_2022 <- read_csv("Desktop/case study 1/202211.csv")
dec_2022 <- read_csv("Desktop/case study 1/202212.csv")
jan_2023 <- read_csv("Desktop/case study 1/202301.csv")
feb_2023 <- read_csv("Desktop/case study 1/202302.csv")

```

## Merging Data Into Single Sheet

```{r Merge}
all_trips <- bind_rows(feb_2022,mar_2022,apr_2022,may_2022,jun_2022,jul_2022,aug_2022,sep_2022,oct_2022,
                       nov_2022,dec_2022,jan_2023,feb_2023)

```

## Clean Up And Add Data To Prepare For Analysis

```{r clean data}
all_trips <- all_trips %>% select(-c(start_lat,start_lng,end_lat,end_lng))

all_trips$ride_length <- difftime(all_trips$ended_at,all_trips$started_at)

all_trips$ride_length <- as.numeric(as.character(all_trips$ride_length))

all_trips$date <- as.Date(all_trips$started_at)
all_trips$month <- format(as.Date(all_trips$date),"%m")
all_trips$day <- format(as.Date(all_trips$date),"%d")
all_trips$year <- format(as.Date(all_trips$date),"%Y")
all_trips$day_of_week <- format(as.Date(all_trips$date),"%A")

all_trips_v2 <- all_trips[!(all_trips$start_station_name == "HQ QR"|all_trips$ride_length<0),] 

```

## Conducting Descriptive Analysis

```{r descriptive analysis on ride length}

summary(all_trips$ride_length)

aggregate(all_trips_v2$ride_length~all_trips_v2$member_casual,FUN = mean)
aggregate(all_trips_v2$ride_length~all_trips_v2$member_casual,FUN = median)
aggregate(all_trips_v2$ride_length~all_trips_v2$member_casual,FUN = max)
aggregate(all_trips_v2$ride_length~all_trips_v2$member_casual,FUN = min)

aggregate(all_trips_v2$ride_length~all_trips_v2$member_casual+all_trips_v2$day_of_week,FUN = mean)
all_trips_v2$day_of_week <- ordered(all_trips_v2$day_of_week,levels = c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday"))
aggregate(all_trips_v2$ride_length~all_trips_v2$member_casual+all_trips_v2$day_of_week,FUN = mean)
```

##Visualisation

Here,we will go through a series of visualization

## Comparing Average_Duration On Weekdays By Member_Casual

```{r average duaration on weekdays, message=FALSE, warning=FALSE}
library(ggplot2)
all_trips_v2 %>% mutate(weekday = wday(started_at,label = TRUE)) %>% 
  group_by(member_casual,weekday) %>% 
  summarise(number_of_rides = n(),average_duration = mean(ride_length)) %>% arrange(member_casual,weekday) %>% 
  ggplot(aes(x = weekday,y = average_duration,fill = member_casual))+geom_col(position = "dodge")
  
```

## Comparing Number Of Rides On Weekdays By Member_Casual

```{r number of rides on weekdays, message=FALSE, warning=FALSE}
all_trips_v2 %>% mutate(weekday = wday(started_at,label = TRUE)) %>% 
  group_by(member_casual,weekday,) %>% 
  summarise(number_of_rides = n(),average_duration = mean(ride_length)) %>% arrange(member_casual,weekday) %>% 
  ggplot(aes(x = weekday,y = number_of_rides,fill = member_casual))+geom_col(position = "dodge")

```

a='mat'
